{memes}: an R interface to the MEME Suite

### 2020-07-28 manuscript.Rmd
more reworking design section

@@

When analyzing ChIP-seq data in R, transcription factor binding locations (ChIP
Peaks) are commonly represented as `GenomicRanges` objects, which contain
genomic positions of each peak, along with an arbitrary number of metadata
columns describing features of each peak.

@@

## Core Utilities

Tools requiring sequences as input can use a path to a .fasta format
file, a `Biostrings::XStringSet`, or a `Biostrings::BStringSetList` as input.
These data structures support all biological sequence types: DNA,
RNA, and amino-acid. For the remainder of the text, we will 
**use chip-seq data analysis as a framework to highlight memes features**
\strikethrough{focus our examples on DNA sequences.}

Some `memes` tools require motifs as input. In these instances, `memes` will
always accept a path to a .meme format file, or a list of motifs in
`universalmotif` format \cite{universalmotif}. The `universalmotif` package
provides simple import and motif conversion functions for all common motif data
structures and file types, ensuring cross-compatability with all commonly used
motif data formats. When `memes` functions return motifs, they are returned to
the user in `universalmotif` format. This ensures that all `memes` motif outputs
can be used as inputs to other `memes` functions that accept motif inputs.
Furthermore, `universalmotif` conversion tools allow `memes` detected motifs to
be used in many other popular Bioconductor motif packages, such as `TFBSTools`
and `motifStack`, providing the user with maximum flexibility in their analysis.

When analyzing ChIP-seq data in R, transcription factor binding locations (ChIP
Peaks) are commonly represented as `GenomicRanges` objects, which contain
genomic positions of each peak, along with an arbitrary number of metadata
columns describing features of each peak.

>>>>

### Core Utilities

@@

**CONTINUE**

MEME Suite focuses on sequence data as the centerpoint of analysis, but in the
case of ChIP-seq, data are often stored as genomic coordinates with additional
metadata columns, such as `GRanges` objects in R/Bioconductor.

@@

Furthermore, `universalmotif` conversion tools allow `memes` detected motifs to
be used in many other popular Bioconductor motif packages, such as `TFBSTools`
and `motifStack`, providing the user with maximum flexibility in their analysis.
